### 2024-10-17 analysis/analysis.qmd
reporting valence results (text) revision
new figures in a separate quarto docs

```{r}
#| warning: false
#| eval: true
library(dmetar)
library(tidyverse)
library(meta)
library(DescTools)
library(ggrepel)
```

@@

@@

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = studyREF)

#funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)

>>>>

```{r}
#| warning: false
#| eval: true
library(dmetar,quietly = TRUE)
library(tidyverse,quietly = TRUE)
library(meta)
library(DescTools)
library(ggrepel)
```

@@

### Sub-division based on N features and genres

```{r}
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
dim(tmp)
m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r}
#| fig-width: 12
#| fig-height: 6
fig2a <- forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = studyREF)

fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)

library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = m.cor$TE.common,
                lower = m.cor$lower.common,
                upper = m.cor$upper.common,
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(m.cor$TE.common,2),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
)
)

source('../etc/custom_funnel_plot.R')
fp2 <- custom_funnel_plot(m.cor)

gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
```

### 2024-10-17 analysis/preprocessing.qmd
new figures in a separate quarto docs

R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed))

@@

table(R_studies$feature_n_complexity)
```

>>>>

R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))

@@

table(R_studies$feature_n_complexity)
```
## Feature N and genre split

```{r}
quantile(subset(R_studies,stimulus_genre_mixed=='SingleGenre')$feature_n,probs = seq(0,1,0.333))
quantile(subset(R_studies,stimulus_genre_mixed=='MultiGenre')$feature_n,na.rm=TRUE,probs = seq(0,1,0.333))

# a combination of the two
R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
                                      breaks = c(0,15,501,653,10000),
                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
table(R_studies$feature_n_complexity_genre)
```

### 2024-10-17 manuscript/_figure1.qmd
new figures in a separate quarto docs

```{r}
#| label: fig1
#| fig.height: 7
#| echo: false
#| fig.cap: > 
#|   Forest plot of valence predictions from the MER models.

library(metafor)
library(dmetar)
library(meta)

R_summary <- read.csv("../analysis/R_summary.csv")
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")

# Max values
m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF,#citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 #                 backtransf = TRUE,
                 #                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

forest(m.cor,
       sortvar = TE,
       fontfamily = "Times",
       hetstat =FALSE,
       prediction = FALSE, 
       print.tau2 = FALSE,
       leftlabs = c("Author", "g", "SE"),layout = "meta",addrows =0,rows.gr=0,col.diamond='black') # RevMan5

```

>>>>

```{dot}
//| label: fig1
//| fig-cap: "Flowchart of the study inclusions/eliminations."

digraph sub {
  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
  A [label = "Records identified from:
                Web of Science (n = 142)
                Scopus (n = 227)
                OpenALEX (n = 278)" ]
  B [label = "Records removed before screening: 
                Duplicates entries/errors (n = 94)" ]
  C [label = "Records after duplicates removed (n = 553)"]
  D [label = "Records screened (n = 553)"]
  E [label = "Records removed: 
                Irrelevant titles/themes (n = 338)
                Abstract screening (n = 95)
                Discussion (n = 24)"]
  F [label = "Full text articles assessed (n = 96)"]
  G [label = "Studies included in final review (n = 46)"]
  H [label = "Full text articles excluded
             (n = 50)"]
  I [label = "Studies excluded in final review (n = 10)"]
  J [label = "Final selection (n = 36)"]
  A->B
  A->C
  C->D
  D->E
  D->F
  F->H 
  F->G
  G->I
  G->J

  { rank = same; A B}
  { rank = same; D, E}
  { rank = same; F, H}
  { rank = same; G, I}
}
```

### 2024-10-17 manuscript/_figure2.qmd
new figures in a separate quarto docs

# Analysis

This assumes that the data has been parsed (`parse-model-output.R`, `format-study-results.R`) and preprocessed (`processing.qmd`).

## Regression studies

### Valence: Best model

For creating Table 2

```{r}
#| warning: false
#| eval: true
library(dmetar,quietly = TRUE)
library(tidyverse,quietly = TRUE)
library(meta)
library(DescTools)
library(ggrepel)
```

#### Using all models

```{r}
R_studies <- read.csv("R_studies.csv")
#R_summary <- read.csv("R_summary.csv")

# select regression studies with r2
#tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp <- dplyr::filter(R_studies,dimension=="valence")
#dim(tmp)

#if all studies, remove two with NA values
tmp <- tmp[!is.na(tmp$values),]
#dim(tmp)

# Take all models
m.cor <- metacor(cor = values,     # values 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

print(m.cor)

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))

@@

#### Using the best model out of each study

```{r}
#R_studies <- read.csv("R_studies.csv")
R_summary <- read.csv("R_summary.csv")

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
#tmp <- dplyr::filter(R_studies,dimension=="valence")
#dim(tmp)

#if all studies, remove two
#tmp <- tmp[!is.na(tmp$values),]
#dim(tmp)

## Disambiguate the studies
tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")

print(m.cor)

print(FisherZInv(m.cor$TE.random))
print(FisherZInv(m.cor$upper.random))
print(FisherZInv(m.cor$lower.random))

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))

### Sub-division based on techniques

```{r}
m.cor1 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  model_class_id,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor1)

S<-summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
print(S)
```

### Sub-division based on journals (engineering vs psych)

```{r}
m.cor2 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  journal_type,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
```

### Sub-division based on N features

```{r}
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
dim(tmp)
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

### Sub-division based on N features and genres

```{r}
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
dim(tmp)
m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(S)

#### Visualise (forest and funnel plots)

```{r}
#| fig-width: 12
#| fig-height: 6
fig2a <- forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = studyREF)

fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)

library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

source('../etc/custom_funnel_plot.R')
fp2 <- custom_funnel_plot(m.cor)

gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
```

#### Explore qualities (in progress)

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
infan <- InfluenceAnalysis(m.cor)
print(eggers.test(m.cor))
```

#### Re-run the analysis without the outliers

```{r}
#| eval: false
#| echo: false
outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")

tmp2<-tmp[!tmp$unique_id %in% outliers,]
m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id, # unique_id
                 data = tmp2,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 prediction = TRUE,
                 backtransf = TRUE,
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

print(m.cor)

fp <- funnel(m.cor, common = TRUE,studlab=FALSE)

#### Custom funnel plot

To show the quality differences between core and eliminated studies.

```{r}
tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
#tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)

estimate = m.cor$TE.common
se = m.cor$seTE.common
se.seq=seq(0, max(m.cor$cor), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

fp = ggplot(NULL) +
  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
  geom_text_repel(aes(x = SE, y = Zr, label=studies), data=tmpdata,size=2.5,max.overlaps = 40)+
  xlab('Standard Error') + ylab('Correlation')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_hline(yintercept = estimate, linetype='solid', color='grey50',linewidth=0.2) +
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
  scale_y_continuous(breaks=seq(0.0,1.00,0.20),limits=c(0.0,1.00),expand=c(0.00,0.00))+
  coord_flip()+
  theme_bw()
print(fp)
```

#### Subgroup analysis according to techniques

add `journal_type` and `stimulus_genre_mixed` as a grouping option

```{r}
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

print(m.cor_subgroups)
#forest(m.cor_subgroups,subgroup=TRUE)
```

- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### Arousal: Best model

```{r}
#| warning: false
#| eval: true

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
#tmp <- dplyr::filter(R_studies,dimension=="arousal")
dim(tmp)
#tmp <- tmp[!is.na(tmp$values),]
dim(tmp)
#tmp<-drop_na(tmp)

m.cor <- metacor(cor = valuesMax, 
                 n = stimulus_n,
                 studlab = citekey,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

print(m.cor)
```
### Trimmed analysis
```{r}
O <- find.outliers(m.cor)
```

#### Visualise (forest and funnel plots)

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))
plot(eggers.test(m.cor))
```

#### Explore qualities (in progress)

```{r}
#| eval: false
meta <- metagen(valuesMax, sqrt(valuesMax), 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")
find.outliers(meta)
infan <- InfluenceAnalysis(meta)
print(eggers.test(meta))

#### Subgroup analysis according to techniques

```{r}
update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)

forest(m.cor_subgroups,subgroup=TRUE)
```

- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

```{r}
#| eval: false
g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
   geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
   coord_flip()+
   theme_bw()
g1

# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
# g<-ggplot(S,aes(y=maxvalue))+
#   geom_histogram(bins = 14)+
#   #facet_wrap(.~studyREF)+
#   coord_flip()+
#   theme_bw()
# g
```

## Classification studies

```{r}
#| warning: false
#| eval: true

C_studies <- read.csv("C_studies.csv")
C_studies <- C_studies[!is.na(C_studies$values),]

C_summary <- read.csv("C_summary.csv")

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = studyREF, # unique_id
                 data = C_summary,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

#print(m.cor)

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))

```
#### Custom plot

```{r}
library(ggrepel)
tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)

tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
tmpdata$citekey<-factor(tmpdata$citekey)

g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
  geom_point(show.legend = FALSE) +
  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
  ylab('Standard Error') + 
  xlab('r')+
  scale_y_reverse()+
#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
#  coord_flip()+
  theme_bw()
print(g)
```

#### Visualise (forest and funnel plots)

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = citekey)

funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)

#### Explore qualities (in progress)

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
#infan <- InfluenceAnalysis(m.cor)
#print(eggers.test(m.cor))

#### Re-run the analysis without the outliers

```{r}
#| eval: false
#| echo: false
outliers <- c("")

tmp2<-tmp[!tmp$unique_id %in% outliers,]
m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id, # unique_id
                 data = tmp2,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 prediction = TRUE,
                 backtransf = TRUE,
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

print(m.cor)

fp <- funnel(m.cor, common = TRUE,studlab=FALSE)

#### Custom funnel plot

To show the quality differences between core and eliminated studies (in progress).

```{r}
#| eval: true
tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)

tmpdata$studyREF <- substr(tmpdata$studies,1,nchar(tmpdata$studies)-2)
tmpdata$studyREF <- str_replace_all(tmpdata$studyREF,'([0-9]+)',' et al \\1')
tmpdata$studyREF <- str_to_sentence(tmpdata$studyREF)
tmpdata$studyREF

estimate = m.cor$TE.common
se = m.cor$seTE.common
se.seq=seq(0, max(m.cor$cor), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

fp = ggplot(NULL) +
  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
  geom_text_repel(aes(x = SE, y = Zr, label=studyREF), data=tmpdata,size=2.5,max.overlaps = 40)+
  xlab('Standard Error') + ylab('Fisher\'s z transformed correlation')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
#  scale_x_reverse()+
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
  coord_flip()+
  theme_bw()
print(fp)

#### Subgroup analysis according to techniques

add `journal_type` and `stimulus_genre_mixed` as a grouping option

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

print(m.cor_subgroups)
#forest(m.cor_subgroups,subgroup=TRUE)
```

- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

>>>>

```{r}
#| label: fig2
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest and funnel plots of valence predictions from the MER models.

library(metafor, warn.conflicts = FALSE)
library(dmetar,warn.conflicts = FALSE)
library(meta,warn.conflicts = FALSE)
library(DescTools,warn.conflicts = FALSE)
library(ggplot2,quietly = TRUE)
library(ggrepel,quietly = TRUE)

R_summary <- read.csv("../analysis/R_summary.csv")
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")

#### Forest plot using forestplot
library(forestplot)
data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
data<-dplyr::arrange(data,mean)

#### Funnel plot using a custom function
source('../etc/custom_funnel_plot.R')
fp2 <- suppressWarnings(custom_funnel_plot(m.cor))

gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))

@@

### 2024-10-17 manuscript/manuscript.qmd
new figures in a separate quarto docs

\[Figure 1: flowchart of the study inclusions/eliminations\]

```{dot}

digraph sub {
  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
  A [label = "Records identified from:
                Web of Science (n = 142)
                Scopus (n = 227)
                OpenALEX (n = 278)" ]
  B [label = "Records removed before screening: 
                Duplicates entries/errors (n = 94)" ]
  C [label = "Records after duplicates removed (n = 553)"]
  D [label = "Records screened (n = 553)"]
  E [label = "Records removed: 
                Irrelevant titles/themes (n = 338)
                Abstract screening (n = 95)
                Discussion (n = 24)"]
  F [label = "Full text articles assessed (n = 96)"]
  G [label = "Studies included in final review (n = 46)"]
  H [label = "Full text articles excluded
             (n = 50)"]
  I [label = "Studies excluded in final review (n = 10)"]
  J [label = "Final selection (n = 36)"]
  A->B
  A->C
  C->D
  D->E
  D->F
  F->H 
  F->G
  G->I
  G->J

  { rank = same; A B}
  { rank = same; D, E}
  { rank = same; F, H}
  { rank = same; G, I}
}

```

@@

-   OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION
<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->

@@

@@

These comparisons of sub-groupings are also influenced by other factors, such as the type of stimuli used in the studies and whether the objective is to explain or predict emotions. Although the sub-groupings result in an uneven distribution of studies and observations, they still offer valuable insights. Despite these caveats, the current sub-groupings enable us to identify interesting differences related to model success across the studies.

@@

Figure 2. Forest plot of arousal prediction (using Max?)

<!-- | Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% | -->

<!-- | Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% | -->

<!-- | Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% | -->

<!-- | Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% | -->

>>>>

@@

@@

{{< include _figure2.qmd >}}

@@

We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in model success might lie. For this purpose, we grouped the studies into small single genre/multigenre studies (1), medium single genre/multigenre studies (2), and medium-large single genre/multigenre studies (3), and huge multigenre studies (4). The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708). The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).

<!-- However, these analyses did not reveal any clear patterns, likely due to the small number of studies in each subgroup.  -->

<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->

These comparisons of sub-groupings are also influenced by other factors, such as the type of journal (psychology vs engineering) or whether the objective is to explain or predict emotions. Although the sub-groupings result in an uneven distribution of studies and observations, they still offer valuable insights. Despite these caveats, the  two main sub-groupings portrayed in Table 2 enable us to identify valuable differences related to model success across the studies.

@@

<!-- {{< include _figure3.qmd >}} -->
